\section{\textsf{Functional Equations}}
\subsection{Problems}
\subsubsection{Kyrgzstan 2012 02/13/26}
\begin{problem}
Find all functions $ f:\RR\to\RR $ such that
\[
	f(f(x)^2+f(y)) = xf(x)+y \quad \forall x,y\in \RR
\]
\end{problem}
We claim that $f(x)=\pm x$ is the only possible solution. It is clear to see that $f(x)=\pm x$ indeed works.
Now we prove it is the only two functions that actually work.

\begin{claim}
	The function $f$ is bijective.
\end{claim}
\begin{proof}
	Plugging $x=0$ gives
	\[
		f(f(0)^2+f(0))=0,
	\]
	and plugging $u=f(0)^2+f(0)$ gives $f(u)=0$. Hence, we can say $x=u$ to find that
	\[
		f(f(y))=y. \qedhere
	\]
\end{proof}
Say $f(t)=x$. Hence,
\[
	f(t^2+f(y))=f(t)\cdot t + y= f(f(t)^2+f(y)) \iff f(t)^2=t^2.
\]
However, we must still escape the pointwise trap!

By the sake of contradiction, say the function $f$ isn't one of the two linear functions we found out. Hence, say
$f(a)=+a$ and $f(b)=-b$. Thus,
\[
	f(a^2-b)=a^2+b.
\]
Contradiction! $a$ and $b$ aren't equal 0 at the same time.


\clearpage

\subsubsection{02/14/26}
\begin{problem}
Find all functions $f:\mathbb{R}\to\mathbb{R}$ such that
\[
	f(x^{2}+y)=f(x^{27}+2y)+f(x^{4})
\]
for all $x,y\in\mathbb{R}$.
\end{problem}
We claim the answer is $f(x)=0$. Clearly it works, so we demonstrate now that it is the only possible answer.

Say $x^2+y=x^{27}+2y$. Hence,
\[
	f(2x^2-x^{27})=f(2x^2-x^{27})+f(x^4) \iff f(x^4)=0.
\]
Thus, $f(x)=0$ for all nonnegative numbers. To prove the same is true for negative numbers and $0$,
we must simply say $y=0$, resulting in $f(x^{27})=0$.

\clearpage

\subsubsection{02/16/26}
\begin{problem}
Find all strictly increasing functions $f:\mathbb{Z}\to\mathbb{Z}$ such that
\[
	f(f(x))=x+2
\]
for all integers $x$.
\end{problem}
We claim the answer is $f(x)=x+1$, which clearly works. Now, we demonstrate it is the only answer.

Since $f(f(x))=x+2$,
\[
	f(f(f(x)))=f(x+2).
\]
At the same time, by saying that $f(x)=x$, we have
\[
	f(f(f(x)))=f(x)+2.
\]
Hence,
\[
	f(x+2)=f(f(f(x)))=f(x)+2.
\]

Since, $f(x)<f(x+1)<f(x+2)$ and $f: \ZZ \to \ZZ$,
\[
	f(x+1)=f(x)+1 \quad \text{and} \quad f(x)=x+f(0).
\]
Since $f(x)=x+1$ works, $f(0)=1$. Hence, the only possible answer is
\[
	f(x)=x+1.
\]

\clearpage

\subsubsection{02/16/26}
\begin{problem}
Find all functions $f:\mathbb{R}\to\mathbb{R}$ such that
\[
	x f(x) + y^{2} + f(xy) = f(x+y)^{2} - f(x)f(y).
\]
for all real numbers $x$ and $y$.
\end{problem}

We claim the answer is $f(x)=x$, which is clearly true. Now, we prove it is the only answer.

After replacing $x$ and $y$ and subtracting the replacements, we find
\[
	xf(x)-x^2=yf(y)-y^2 \iff g(x)=g(y).
\]
Hence, $g(x)$ is a constant $c$. Say $x=0 \iff c=0$. Hence,
\[
	xf(x)=x^2 \iff f(x)=x
\]
for every $x \neq 0$. Now, taking $x=y=0$ in the original equation, we find $f(0)=0$.

\clearpage

\subsubsection{Cauchy's funcitonal equation over $\QQ$ 02/16/26}
\begin{problem}
\end{problem}
